\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-12-14 popl-2019-journal-v/paper.tex
Oops.. not a functional pearl...
Add file with JFP reviews in order to collect responses, fix trivial typos already.

\newcommand{\trgcm}{\textsc{LCM}}
\newcommand{\srccm}{\textsc{oLCM}}
\newcommand{\extend}[1]{}
\newcommand{\Rel}[1]{\mathrm{Rel}(#1)}
\newcommand{\fers}[1][n]{\left(\nequal[#1]\right)_{#1=0}^{\infty}}
\newcommand{\cofe}[2][n]{\left(#2,\fers[#1] \right)}
\newcommand{\seq}[2][n]{\left(#2_{#1}\right)_{#1=0}^{\infty}}
\setlength{\belowcaptionskip}{-5pt}

@@

\maketitle[F]

@@

A second contribution of this work is the way in which we formulate these two properties.
Although the terms ``well-bracketed control flow'' and ``local state encapsulation'' sound precise, it is actually far from clear what they mean, and how best to formalize them.
Existing formulations are either partial and not suitable for reasoning~\cite{abadi_control-flow_2005} or lack evidence of generality~\cite{skorstengaard_reasoning_2017}.
We propose a new formulation using a technique we call {\itshape fully abstract overlay semantics}.
It starts from the premise that security results for a calling convention should be reusable as part of a larger proof of a secure compiler.
To this end, we define a second operational semantics for our target language with a native well-bracketed call stack and primitive ways to do calls and returns.
This well-behaved semantics guarantees WBCF and LSE natively for components using our calling convention.
As such, these components can be sure that they will only ever interact with other well-behaved components that respect our desired properties.
To express security of our calling convention, we then show that considering the same components in the original semantics does not give adversaries additional ways to interact with them. 
More formally, we show that mapping a component in the well-behaved semantics to the same component in the original semantics is fully abstract~\cite{abadi_protection_1999}, i.e.\ components are indistinguishable to arbitrary adversaries in the well-behaved language iff they are indistinguishable to arbitrary adversaries in the original language.

@@

On \trgcm{} we have CHERI-like sealed capabilities to achieve this~\cite{watson_cheri_2015,watson_fast_2016}.

@@

In spirit of memory capabilities, a set of seals capability has a current seal $\sigma_{\var{current}}$ that is selected for use in the next seal operation.

@@

%%% Domains
Words on \trgcm{} are capabilities and data (represented by integers $\ints$).
We assume a finite set of register names $\RegName$ containing at least the registers $\pcreg$, $\rretd$, $\rretc$, $\rstk$, $\rdata$, $\rtmp{1}$, and $\rtmp{2}$.
We define register files as functions from register names to words.
Complete memories map all addresses to words and memory segments map some addresses to words (i.e.\ they are partial functions).
$\trgcm{}$ has two terminated configurations $\halted$ and $\failed$ that respectively signify a successful execution and an execution where something went wrong, e.g.,\ an out-of-bounds memory access.
An executable configuration is a register file and memory pair.

@@

  Additionally, when the untrusted code returns,  we need to regain access to the capabilities that represent our authority, which we had access to before passing control.
  To achieve this, we have to store them in a location that we can access after the return.
  However, without an encapsulation mechanism, the untrusted code would have access to all this through the return capability because it gives the same authority to the untrusted code as to us after the return.
  This is why, any reasonable capability machine must have an encapsulation mechanism to allow programs to set up boundaries between security domains.

@@

  Sealing is meant for encapsulation, but it relies on seals being kept private as should be clear from the explanations so far.
  For this reason, it is important that trusted code does not leak its seals to adversaries and that the system is initialised such that each component has access to unique seals.
  We return to this in \sectionname~\ref{sec:well-form-reas}.
\end{jversion}

@@

\subsection{Components, linking, programs, and contexts }
\label{subsec:components-linking}
The executable configuration describes the machine state, but it does not make it clear what components run on the machine and how they interact with each other.
To clarify this, we introduce notions of components and programs from which we construct executable configurations.
A component (defined in Figure~\ref{fig:target-component-and-linking}) is basically a program with entry points in the form of imports that need to be linked.
It has exports that can satisfy the imports of other components.
% Structure
A base component $\comp_0$ consists of a code memory segment, a data memory segment, a list of imported symbols, a list of exported symbols, two lists specifying the available seals (see Section~\ref{sec:form-secur-with}.), and a set of all the linear addresses (addresses governed by a linear capability).
The import list specifies where in memory imports should be placed, and imports are matched to exports via their symbols.
An export associates a word with a symbol.
%base = library
A component is either a library component (without a main entry point) or an incomplete program with a main in the form of a pair of sealed capabilities.
The latter can be seen as a program that still needs to be linked with libraries.
% Linking .
Components are combined into new components by linking them together, as long as only one has a main function.
Two components can be linked when their memories, seals, and linear addresses are disjoint.
They are combined by taking the union of each of their constituents.
For every import that is satisfied by an export of the other component, the data memory is updated to have the exported word on the imported address.
The satisfied imports are removed from the import list in the resulting linked component and the exports are obtained by combining the components' exports.

% Programs
We can now define the notion of a program as well as a context.
\begin{definition}[Programs and Contexts]
  \label{def:program-and-context}
  A \emph{program} is a component $(\comp_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})$ with an empty import list.
  A \emph{context} for a component $\comp$ is a component $\comp'$ such that $\comp \bowtie \comp'$ is a program.
\end{definition}
% Getting an executable from a component - postpone this to later, but mention:
% write xor exec
How a program is initialised to create an executable configuration, is discussed in Section~\ref{sec:form-secur-with}.
% We will, however, at this point mention that all programs will be instrumented as Write-XOR-Execute,{Do we have a reference for this?} i.e.\ there will only be read-execute capabilities for the code and read-write capabilities for the data.
%Further, we will only consider a specific class of well-formed components, but we will get back to this.
Some simplifications have been made in this presentation of \trgcm{}. See \citet{technical_report_popl} for details.
\begin{figure}[tb]
  \centering
  \[
    \begin{array}{rl c rl c rl}
    s &\in \Symbol & \phantom{make} &
    \mathrm{import} &\mathrel{::=} a \mapsfrom s & \phantom{make} &
    \mathrm{export} &\mathrel{::=} s \mapsto w\\
    \comp_0 & \multicolumn{7}{l}{\mathrel{::=} (\mscode,\msdata,\overline{\mathrm{import}},\overline{\mathrm{export}},\sigrets,\sigcloss,A_\linear)}\\
    \comp & \multicolumn{7}{l}{\mathrel{::=} \comp_0 \mid  (\comp_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})}
  \end{array}
\]
\vspace{0.5cm}
\begin{mathpar}
  \inference{
    \comp_0 = (\mscode[1], \msdata[1], \overline{\var{import}_1}, \overline{\var{export}_1}, \sigrets[1], \sigcloss[1],A_{\linear,1})\\
    \comp_0' = (\mscode[2], \msdata[2], \overline{\var{import}_2}, \overline{\var{export}_2}, \sigrets[2], \sigcloss[2],A_{\linear,2})\\
    \comp_0'' = (\mscode[3], \msdata[3], \overline{\var{import}_3}, \overline{\var{export}_3}, \sigrets[3], \sigcloss[3],A_{\linear,3})\\
    \mscode[3] = \mscode[1] \uplus \mscode[2] \\
    \msdata[3] = (\msdata[1] \uplus \msdata[2])[a \mapsto w \mid (a \mapsfrom s) \in (\overline{\var{import}_1} \cup \overline{\var{import}_2}), (s \mapsto w) \in \overline{\var{export}}_3] \\
    \overline{\var{export}_3} = \overline{\var{export}_1} \cup \overline{\var{export}_2}&
    \overline{\var{import}_3} = \{ a \mapsfrom s \in (\overline{\var{import}_1} \cup \overline{\var{import}_2}) \mid s \mapsto \_ \not\in \overline{\var{export}_3} \}\\
    \sigrets[3] = \sigrets[1] \uplus \sigrets[2] &
    \sigcloss[3] = \sigcloss[1] \uplus \sigcloss[2] &
    A_{\linear,3} = A_{\linear,1} \uplus A_{\linear,2}\\
    \dom(\mscode[3]) \mathrel{\#} \dom(\msdata[3]) & \sigrets[3] \mathrel{\#} \sigcloss[3]
  } {
    \comp_0'' = \comp_0 \bowtie \comp_0'
  }
  \and
  \inference{
    \comp_0'' = \comp_0 \bowtie \comp_0'
  }{
    \begin{aligned}
      (\comp_0'',c_{\mathrm{main},c}, c_{\mathrm{main},d}) &= \comp_0 \bowtie
      (\comp_0',c_{\mathrm{main},c}, c_{\mathrm{main},d})\\
      &=
      (\comp_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}) \bowtie \comp_0'
    \end{aligned}
  }
  \end{mathpar}
% \begin{definition}[Plugging a program into a context]
%   When $\var{comp'}$ is a context for component $\comp$ and $\comp' \bowtie \comp \rightsquigarrow \Phi$, 
%   then we write $\plug{\comp'}{\comp}$ for the execution configuration $\Phi$.
% \end{definition}
  \caption{Components and linking of components.}
  \label{fig:target-component-and-linking}
\end{figure}

@@

Ideally, we would like to define the properties in a way that is
\begin{enumerate}
\item {\itshape intuitive} \label{def-prop:intuitive}
\item {\itshape useful for reasoning:} we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}. \label{def-prop:useful}
\item {\itshape reusable in secure compiler chains:} for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.\label{def-prop:reusable}
\item {\itshape arguably "complete"}: the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. \label{def-prop:complete}
\item {\itshape potentially scalable}: although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.\label{def-prop:scalable}
\end{enumerate}

@@

The main difference between the two semantics, is that the new one satisfies LSE and WBCF by construction: the abstract machine comes with a built-in stack, inactive stack frames are unaddressable and well-bracketed control flow is built-in to the abstract machine.
Important run-time values like return capabilities and stack pointers are represented by special syntactic tokens that interact with the abstract machine's stack, but during execution, there remains a close, structural correspondence to the actual regular capabilities that they represent.
For example, stack capabilities in the overlay semantics correspond directly to linear capabilities in the underlying semantics, and they have authority over the part of memory that the overlay views as the stack.
\begin{jversion}
The new run-time values in the overlay semantics are treated appropriately in functions like $\encType{}$.
All the new values correspond to concrete capabilities on the \trgcm{} machine which the encoding function reflects.
For instance, the encoding of a stack pointer in the overlay semantics is the same as the encoding of a linear memory capability on the \trgcm{} machine.
\end{jversion}

The fact that \stktokens{} enforces LSE and WBCF is then formulated as a theorem about the function that maps components in the well-behaved overlay semantics to the underlying components in the regular semantics.
The theorem states that this function constitutes a fully abstract compiler, a well-known property from the field of secure compilation~\cite{abadi_protection_1999}.
Intuitively, the theorem states that if a trusted component interacts with (potentially malicious) components in the regular semantics, then these components have no more expressive power than components which the trusted component interacts with in the well-behaved overlay semantics.
In other words, they cannot do anything that doesn't correspond to something that a well-behaved component, respecting LSE and WBCF, can also do.
More formally, our full-abstraction result states that two trusted components are indistinguishable to arbitrary other components in the regular semantics if and only if they are indistinguishable to arbitrary other components in the overlay semantics.

Our formal results are complicated by the fact that they only hold on a sane initial configuration of the system and for components that respect the basic rules of the calling convention.
For example, the system should be set up such that seals used by components for constructing return pointers are not shared with other components.
We envision distributing seals as a job for the linker, so this means our results depend on the linker to do this properly.
As another example, a seal used to construct a return pointer can be reused but only to construct return pointers for the same return point.
Different seals must be used for different return points.
Such seals should also never be passed to other components.
These requirements are easy to satisfy: components should request sufficient seals from the linker, use a different one for every place in the code where they make a call to another component, and make sure to clear them from registers before every call.
The general pattern is that $\stktokens{}$ only protects components that do not shoot themselves in the foot by violating a few basic rules.
In this section, we define a well-formedness judgement for the syntactic requirements on components as well as a reasonability condition that semantically disallows components to do certain unsafe things.
Well-formedness is a requirement for all components (trusted and untrusted), but the reasonability requirement only applies to trusted components, i.e.\ those components for which we provide LSE and WBCF guarantees.

@@

\end{jversion}
\subsection{Reasonable Components}
\label{sec:reasonable-components}
% Reasonability
The static guarantees given by $\wdjud[\ta]{\comp}$ makes sure that components initially don't undermine the security measures needed for \stktokens{}, but it does not prevent a trusted component from doing something silly during execution that undermines \stktokens{}.
In order for \stktokens{} to provide guarantees for a component, we expect it to not shoot itself in the foot and perform certain necessary checks not captured by the call code (Figure~\ref{fig:call-code}).
More precisely, we expect four things of a reasonable component:
\begin{enumerate}[label=(\arabic*)]
\item It checks the stack base address before performing a call.
As explained in Section~\ref{sec:stktokens-explained}, we do not include this check in the call code as it often would be redundant.
\item It uses the return seals only for calls and the closure seals in an appropriate way which means that they should only be used to seal executable capabilities for code that behaves reasonably or non-executable things that do not undermine the security mechanisms \stktokens{} relies on.
\item It does not leak return and closure seals (or means to retrieve them).
This means that sets of seals with return or closure seals cannot be left in registers when transferring control to another module.
There are also indirect ways to leak seals such as leaking a capability for code memory or leaking a capability for code memory sealed with an unknown seal.
\item It never stores return and closure seals (or means to get them) to memory.
By disallowing this, we make sure that data memory always can be safely shared as it does not contain seals or means to get them to begin with.
\end{enumerate}
\begin{jversion}
  We capture these properties in 4 definitions.
  Definition~\ref{def:reasonable-word} defines the reasonable words which means that they cannot be used to leak seals directly or indirectly.
  Definition~\ref{def:reasonable-pc} defines the reasonable pc's which means that if it is plugged into a configuration with a register file filled with reasonable words, then the configuration behaves reasonably.
  Definition~\ref{def:reasonable-conf} defines the reasonable configurations which captures the four informal behavioural properties.
  Finally, definition~\ref{def:reasonable-component} lifts the notion of reasonability to components.

  \subsubsection{Reasonable words}
  To provide any guarantees, \stktokens{} rely on the program to no leak return seals in any way.
  But what does it mean to ``leak'' a return seal?
  It means that sets of seals that contain return seals as well as any means to obtain such sets cannot be leaked.
  The following definition makes this more precise.
\begin{definition}[Reasonable word]
  \label{def:reasonable-word}
  Take a set of trusted addresses $\ta$ and sets of return and closure seals $\gsigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ and
free stack $\ms_\stk$ if $n=0$
or the following implications hold.
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then
    $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$
  \item If $w = ((\perm,\_),\baddr,\eaddr,\_)$, then $[\baddr,\eaddr] \mathrel{\#} \ta$
  \item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\gsigrets\cup
    \gsigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
  \item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$
    and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all
    $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
  \item If $w = \stkptr{\perm,\baddr,\eaddr,\_}$ and $\perm \in \readAllowed{}$
    and $n > 0$, then $\ms_\stk(\aaddr)$ is reasonable up to $n - 1$ steps for
    all $\aaddr \in [\baddr,\eaddr]$
  \end{itemize}
\end{definition}
According to the definition, sets of seals that contain return or closure seals are not reasonable.
\stktokens{} rely on return seals to be unique in order to work, but it does not rely on closure seals.
However, it defeats the purpose of the closure seals if they are leaked to malicious code as it allows the malicious code to fabricate data capabilities for the code capabilities or code capabilities for the data capabilities which effectually allows malicious code to unseal the data capability.
Further, it makes reasoning about leakage of return seals difficult because the closures have to be well-behaved no matter what data they are executed with.

@@

    We have that $\Phi$ is reasonable up to $n$ steps.

@@

      for some $\src{r_1}$ and $\src{r_2}$,

@@

        \item $\Phi$ does not point to $\src{\txjmp{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$
        \item $\Phi$ does not point to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ for some $\src{r_1}$ and $\src{r_2}$, $\offpc$, $\offsigma$

@@

A well-formed component makes sure that a return seal is uniquely available to every call.
This is, however, not sufficient as it does not ensure that other parts of a program don't use the return seals.
We do not want to specify what non-call code should look like, so we just require it to not use the call seals.
This is what Item~\ref{item:return-seal-usage} ensures.
It says that if the configuration points to a seal-instruction, then either the instruction is part of a call and uses a return seal or the instruction seals part of a closure and uses a closure seal.
In order to construct a closure, one must seal a code capability and a data capability.
If this is an executable capability, then it should be reasonable as a pc.
On the other hand, if it is not an executable capability, then this must be the data part of the pair, so it should just be a reasonable word.
Definition~\ref{def:reasonable-conf} is cyclic through Definition~\ref{def:reasonable-pc}, so both definitions are step-indexed to break the cycle.

>>>>

\newcommand{\trgcm}{\textsc{LCM}}
\newcommand{\srccm}{\textsc{oLCM}}
\newcommand{\extend}[1]{}
\newcommand{\Rel}[1]{\mathrm{Rel}(#1)}
\newcommand{\fers}[1][n]{\left(\nequal[#1]\right)_{#1=0}^{\infty}}
\newcommand{\cofe}[2][n]{\left(#2,\fers[#1] \right)}
\newcommand{\seq}[2][n]{\left(#2_{#1}\right)_{#1=0}^{\infty}}
% \setlength{\belowcaptionskip}{-5pt}

@@

\maketitle

@@

A second contribution of this work is the way in which we formulate these two properties.
Although the terms ``well-bracketed control flow'' and ``local state encapsulation'' sound precise, it is actually far from clear what they mean, and how best to formalize them.
Existing formulations are either partial and not suitable for reasoning~\citep{abadi_control-flow_2005} or lack evidence of generality~\citep{skorstengaard_reasoning_2017}.
We propose a new formulation using a technique we call {\itshape fully abstract overlay semantics}.
It starts from the premise that security results for a calling convention should be reusable as part of a larger proof of a secure compiler.
To this end, we define a second operational semantics for our target language with a native well-bracketed call stack and primitive ways to do calls and returns.
This well-behaved semantics guarantees WBCF and LSE natively for components using our calling convention.
As such, these components can be sure that they will only ever interact with other well-behaved components that respect our desired properties.
To express security of our calling convention, we then show that considering the same components in the original semantics does not give adversaries additional ways to interact with them. 
More formally, we show that mapping a component in the well-behaved semantics to the same component in the original semantics is fully abstract~\citep{abadi_protection_1999}, i.e.\ components are indistinguishable to arbitrary adversaries in the well-behaved language iff they are indistinguishable to arbitrary adversaries in the original language.

@@

On \trgcm{} we have CHERI-like sealed capabilities to achieve this~\citep{watson_cheri_2015,watson_fast_2016}.

@@

In the spirit of memory capabilities, a set of seals capability has a current seal $\sigma_{\var{current}}$ that is selected for use in the next seal operation.

@@

%%% Domains
Words on \trgcm{} are either capabilities or data (represented by integers $\ints$).
We assume a finite set of register names $\RegName$ containing at least the registers $\pcreg$, $\rretd$, $\rretc$, $\rstk$, $\rdata$, $\rtmp{1}$, and $\rtmp{2}$.
We define register files as functions from register names to words.
Complete memories map all addresses to words and memory segments map some addresses to words (i.e.\ they are partial functions).
$\trgcm{}$ has two terminated configurations $\halted$ and $\failed$ that respectively signify a successful execution and an execution where something went wrong, e.g.,\ an out-of-bounds memory access.
An executable configuration is a register file and memory pair.

@@

  Additionally, when the untrusted code returns,  we need to regain access to the capabilities that represent our authority, which we had access to before passing control.
  To achieve this, we have to store them in a location that we can access after the return.
  However, without an encapsulation mechanism, the untrusted code would have access to all this through the return capability because it gives the same authority to the untrusted code as to us after the return.
  This is why any reasonable capability machine must have an encapsulation mechanism to allow programs to set up boundaries between security domains.

@@

  Sealing is meant for encapsulation, but it relies on seals being kept private as should be clear from the explanations so far.
  For this reason, it is important that trusted code does not leak its seals to adversaries and that the system is initialised so that each component has access to unique seals.
  We return to this in \sectionname~\ref{sec:well-form-reas}.
\end{jversion}

@@

\subsection{Components, linking, programs, and contexts }
\label{subsec:components-linking}
The executable configuration describes the machine state, but it does not make it clear what components run on the machine and how they interact with each other.
To clarify this, we introduce notions of components and programs from which we construct executable configurations.
A component (defined in Figure~\ref{fig:target-component-and-linking}) is basically a program with entry points in the form of imports that need to be linked.
It has exports that can satisfy the imports of other components.
% Structure
A base component $\comp_0$ consists of a code memory segment, a data memory segment, a list of imported symbols, a list of exported symbols, two lists specifying the available seals (see Section~\ref{sec:form-secur-with}), and a set of all the linear addresses (addresses governed by a linear capability).
The import list specifies where in memory imports should be placed, and imports are matched to exports via their symbols.
An export associates a word with a symbol.
%base = library
A component is either a library component (without a main entry point) or an incomplete program with a main in the form of a pair of sealed capabilities.
The latter can be seen as a program that still needs to be linked with libraries.
% Linking .
Components are combined into new components by linking them together, as long as only one has a main function.
Two components can be linked when their memories, seals, and linear addresses are disjoint.
They are combined by taking the union of each of their constituents.
For every import that is satisfied by an export of the other component, the data memory is updated to have the exported word on the imported address.
The satisfied imports are removed from the import list in the resulting linked component and the exports are obtained by combining the components' exports.

% Programs
We can now define the notion of a program as well as a context.
\begin{definition}[Programs and Contexts]
  \label{def:program-and-context}
  A \emph{program} is a component $(\comp_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})$ with an empty import list.
  A \emph{context} for a component $\comp$ is a component $\comp'$ such that $\comp \bowtie \comp'$ is a program.
\end{definition}
% Getting an executable from a component - postpone this to later, but mention:
% write xor exec
How a program is initialised to create an executable configuration is discussed in Section~\ref{sec:form-secur-with}.
% We will, however, at this point mention that all programs will be instrumented as Write-XOR-Execute,{Do we have a reference for this?} i.e.\ there will only be read-execute capabilities for the code and read-write capabilities for the data.
%Further, we will only consider a specific class of well-formed components, but we will get back to this.
Some simplifications have been made in this presentation of \trgcm{}. See \citet{technical_report_popl} for details.
\begin{figure}[tb]
  \centering
  \[
    \begin{array}{rl c rl c rl}
    s &\in \Symbol & \phantom{make} &
    \mathrm{import} &\mathrel{::=} a \mapsfrom s & \phantom{make} &
    \mathrm{export} &\mathrel{::=} s \mapsto w\\
    \comp_0 & \multicolumn{7}{l}{\mathrel{::=} (\mscode,\msdata,\overline{\mathrm{import}},\overline{\mathrm{export}},\sigrets,\sigcloss,A_\linear)}\\
    \comp & \multicolumn{7}{l}{\mathrel{::=} \comp_0 \mid  (\comp_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})}
  \end{array}
\]
\vspace{0.5cm}
\begin{mathpar}
  \inference{
    \comp_0 = (\mscode[1], \msdata[1], \overline{\var{import}_1}, \overline{\var{export}_1}, \sigrets[1], \sigcloss[1],A_{\linear,1})\\
    \comp_0' = (\mscode[2], \msdata[2], \overline{\var{import}_2}, \overline{\var{export}_2}, \sigrets[2], \sigcloss[2],A_{\linear,2})\\
    \comp_0'' = (\mscode[3], \msdata[3], \overline{\var{import}_3}, \overline{\var{export}_3}, \sigrets[3], \sigcloss[3],A_{\linear,3})\\
    \mscode[3] = \mscode[1] \uplus \mscode[2] \\
    \msdata[3] = (\msdata[1] \uplus \msdata[2])[a \mapsto w \mid (a \mapsfrom s) \in (\overline{\var{import}_1} \cup \overline{\var{import}_2}), (s \mapsto w) \in \overline{\var{export}}_3] \\
    \overline{\var{export}_3} = \overline{\var{export}_1} \cup \overline{\var{export}_2}&
    \overline{\var{import}_3} = \{ a \mapsfrom s \in (\overline{\var{import}_1} \cup \overline{\var{import}_2}) \mid s \mapsto \_ \not\in \overline{\var{export}_3} \}\\
    \sigrets[3] = \sigrets[1] \uplus \sigrets[2] &
    \sigcloss[3] = \sigcloss[1] \uplus \sigcloss[2] &
    A_{\linear,3} = A_{\linear,1} \uplus A_{\linear,2}\\
    \dom(\mscode[3]) \mathrel{\#} \dom(\msdata[3]) & \sigrets[3] \mathrel{\#} \sigcloss[3]
  } {
    \comp_0'' = \comp_0 \bowtie \comp_0'
  }
  \and
  \inference{
    \comp_0'' = \comp_0 \bowtie \comp_0'
  }{
    \begin{aligned}
      (\comp_0'',c_{\mathrm{main},c}, c_{\mathrm{main},d}) &= \comp_0 \bowtie
      (\comp_0',c_{\mathrm{main},c}, c_{\mathrm{main},d})\\
      &=
      (\comp_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}) \bowtie \comp_0'
    \end{aligned}
  }
  \end{mathpar}
% \begin{definition}[Plugging a program into a context]
%   When $\var{comp'}$ is a context for component $\comp$ and $\comp' \bowtie \comp \rightsquigarrow \Phi$, 
%   then we write $\plug{\comp'}{\comp}$ for the execution configuration $\Phi$.
% \end{definition}
  \caption{Components and linking of components.}
  \label{fig:target-component-and-linking}
\end{figure}

@@

Ideally, we would like to define the properties in a way that is
\begin{enumerate}
\item {\itshape intuitive} \label{def-prop:intuitive}
\item {\itshape useful for reasoning:} we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}. \label{def-prop:useful}
\item {\itshape reusable in secure compiler chains:} for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when proving correctness and security of other compiler passes and then compose such results with ours to obtain results about the full compiler.\label{def-prop:reusable}
\item {\itshape arguably ``complete''}: the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. \label{def-prop:complete}
\item {\itshape potentially scalable}: although dynamic code generation and multi-threading are currently out of scope, the formalization should, at least potentially, extend to such settings.\label{def-prop:scalable}
\end{enumerate}

@@

The main difference between the two semantics is that the new one satisfies LSE and WBCF by construction: the abstract machine comes with a built-in stack, inactive stack frames are unaddressable and well-bracketed control flow is built-in to the abstract machine.
Important run-time values like return capabilities and stack pointers are represented by special syntactic tokens that interact with the abstract machine's stack, but during execution, there remains a close, structural correspondence to the actual regular capabilities that they represent.
For example, stack capabilities in the overlay semantics correspond directly to linear capabilities in the underlying semantics, and they have authority over the part of memory that the overlay views as the stack.
\begin{jversion}
The new run-time values in the overlay semantics are treated appropriately in functions like $\encType{}$.
All the new values correspond to concrete capabilities on the \trgcm{} machine which the encoding function reflects.
For instance, the encoding of a stack pointer in the overlay semantics is the same as the encoding of a linear memory capability on the \trgcm{} machine.
\end{jversion}

The fact that \stktokens{} enforces LSE and WBCF is then formulated as a theorem about the function that maps components in the well-behaved overlay semantics to the underlying components in the regular semantics.
The theorem states that this function constitutes a fully abstract compiler, a well-known property from the field of secure compilation~\citep{abadi_protection_1999}.
Intuitively, the theorem states that if a trusted component interacts with (potentially malicious) components in the regular semantics, then these components have no more expressive power than components which the trusted component interacts with in the well-behaved overlay semantics.
In other words, they cannot do anything that doesn't correspond to something that a well-behaved component, respecting LSE and WBCF, can also do.
More formally, our full-abstraction result states that two trusted components are indistinguishable to arbitrary other components in the regular semantics if and only if they are indistinguishable to arbitrary other components in the overlay semantics.

Our formal results are complicated by the fact that they only hold on a sane initial configuration of the system and for components that respect the basic rules of the calling convention.
For example, the system should be set up so that seals used by components for constructing return pointers are not shared with other components.
We envision distributing seals as a job for the linker, so this means our results depend on the linker to do this properly.
As another example, a seal used to construct a return pointer can be reused but only to construct return pointers for the same return point.
Different seals must be used for different return points.
Such seals should also never be passed to other components.
These requirements are easy to satisfy: components should request sufficient seals from the linker, use a different one for every place in the code where they make a call to another component, and make sure to clear them from registers before every call.
The general pattern is that $\stktokens{}$ only protects components that do not shoot themselves in the foot by violating a few basic rules.
In this section, we define a well-formedness judgement for the syntactic requirements on components as well as a reasonability condition that semantically disallows components to do certain unsafe things.
Well-formedness is a requirement for all components (trusted and untrusted), but the reasonability requirement only applies to trusted components, i.e.\ those components for which we provide LSE and WBCF guarantees.

@@

\end{jversion}
\subsection{Reasonable Components}
\label{sec:reasonable-components}
% Reasonability
The static guarantees given by $\wdjud[\ta]{\comp}$ make sure that components initially don't undermine the security measures needed for \stktokens{}, but it does not prevent a trusted component from doing something silly during execution that undermines \stktokens{}.
In order for \stktokens{} to provide guarantees for a component, we expect it not to shoot itself in the foot and perform certain necessary checks not captured by the call code (Figure~\ref{fig:call-code}).
More precisely, we expect four things of a reasonable component:
\begin{enumerate}[label=(\arabic*)]
\item It checks the stack base address before performing a call.
As explained in Section~\ref{sec:stktokens-explained}, we do not include this check in the call code as it often would be redundant.
\item It uses the return seals only for calls and the closure seals in an appropriate way which means that they should only be used to seal executable capabilities for code that behaves reasonably or non-executable things that do not undermine the security mechanisms \stktokens{} relies on.
\item It does not leak return and closure seals (or means to retrieve them).
This means that sets of seals with return or closure seals cannot be left in registers when transferring control to another module.
There are also indirect ways to leak seals such as leaking a capability for code memory or leaking a capability for code memory sealed with an unknown seal.
\item It never stores return and closure seals (or means to get them) to memory.
By disallowing this, we make sure that data memory always can be safely shared as it does not contain seals or means to get them to begin with.
\end{enumerate}
\begin{jversion}
  We capture these properties in 4 definitions.
  Definition~\ref{def:reasonable-word} defines the reasonable words which means that they cannot be used to leak seals directly or indirectly.
  Definition~\ref{def:reasonable-pc} defines the reasonable PCs which means that if it is plugged into a configuration with a register file filled with reasonable words, then the configuration behaves reasonably.
  Definition~\ref{def:reasonable-conf} defines the reasonable configurations which captures the four informal behavioural properties.
  Finally, definition~\ref{def:reasonable-component} lifts the notion of reasonability to components.

  \subsubsection{Reasonable words}
  To provide any guarantees, \stktokens{} rely on the program not to leak return seals in any way.
  But what does it mean to ``leak'' a return seal?
  It means that sets of seals that contain return seals as well as any means to obtain such sets cannot be leaked.
  The following definition makes this more precise.
\begin{definition}[Reasonable word]
  \label{def:reasonable-word}
  Take a set of trusted addresses $\ta$ and sets of return and closure seals $\gsigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ and
free stack $\ms_\stk$ if $n=0$
or the following implications hold.
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then
    $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$
  \item If $w = ((\perm,\_),\baddr,\eaddr,\_)$, then $[\baddr,\eaddr] \mathrel{\#} \ta$
  \item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\gsigrets\cup
    \gsigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
  \item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$
    and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all
    $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
  \item If $w = \stkptr{\perm,\baddr,\eaddr,\_}$ and $\perm \in \readAllowed{}$
    and $n > 0$, then $\ms_\stk(\aaddr)$ is reasonable up to $n - 1$ steps for
    all $\aaddr \in [\baddr,\eaddr]$
  \end{itemize}
\end{definition}
According to the definition, sets of seals that contain return or closure seals are not reasonable.
\stktokens{} rely on return seals to be unique in order to work, but it does not rely on closure seals.
However, it defeats the purpose of the closure seals if they are leaked to malicious code as it allows the malicious code to fabricate data capabilities for the code capabilities or code capabilities for the data capabilities which effectually allows malicious code to unseal the data capability.
Further, it makes reasoning about leakage of return seals difficult because the closures have to be well-behaved no matter what data they are executed with.

@@

    we have that $\Phi$ is reasonable up to $n$ steps.

@@

      for any $\src{r_1}$ and $\src{r_2}$,

@@

        \item $\Phi$ does not point to $\src{\txjmp{r_1}{r_2}}$ for any $\src{r_1}$ and $\src{r_2}$
        \item $\Phi$ does not point to $\src{\scall{\offpc,\offsigma}{r_1}{r_2}}$ for any $\src{r_1}$ and $\src{r_2}$, $\offpc$, $\offsigma$

@@

A well-formed component makes sure that a return seal is uniquely available to every call.
This is, however, not sufficient as it does not ensure that other parts of a program don't use the return seals.
We do not want to specify what non-call code should look like, so we just require it not to use the call seals.
This is what Item~\ref{item:return-seal-usage} ensures.
It says that if the configuration points to a seal-instruction, then either the instruction is part of a call and uses a return seal or the instruction seals part of a closure and uses a closure seal.
In order to construct a closure, one must seal a code capability and a data capability.
If this is an executable capability, then it should be reasonable as a pc.
On the other hand, if it is not an executable capability, then this must be the data part of the pair, so it should just be a reasonable word.
Definition~\ref{def:reasonable-conf} is cyclic through Definition~\ref{def:reasonable-pc}, so both definitions are step-indexed to break the cycle.
